Where Do Population III Stars Form?

### 2019-05-06 paper.tex
Adjusting Yoshida data

\citet{Yoshida03} used cosmological simulations to study the formation of primordial star-forming clouds. They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds. Importantly, they included \hh{} self-shielding within halos. In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12). They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass at $1.5 \times 10^{6} M_{\odot}$. When \hh{} self-shielding is taken into account along with a LW background, they see these halo masses decrease to $9 \times 10^{6} M_{\odot}$. This value lies close to the case where there is no LW background applied, where the minimum halo mass is $7 \times 10^{5} M_{\odot}$. They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling. In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$. While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}) (this may change !!! ). \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background. They found that \hh{} cooling is dominant even when there is a large LW background present. They included dynamical heating but did not include self-shielding, and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}). Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$. \citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds. They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse. They also ignored \hh{} self-shielding in their calculations and included dynamical heating, which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares). Their halo masses are similar to the results of \citet{Wise07_UVB}. Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.

>>>>

\citet{Yoshida03} used cosmological simulations to study the formation of primordial star-forming clouds. They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds. Importantly, they included \hh{} self-shielding within halos. In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12). They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass is $7 \times 10^{5} M_{\odot}$. When \hh{} self-shielding is taken into account along with a LW background, they see their minimum halo mass decrease to $4.5 \times 10^{5} M_{\odot}$. This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$. They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling. In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$. While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}). \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background. They found that \hh{} cooling is dominant even when there is a large LW background present. They included dynamical heating but did not include self-shielding, and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}). Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$. \citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds. They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse. They also ignored \hh{} self-shielding in their calculations and included dynamical heating, which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares). Their halo masses are similar to the results of \citet{Wise07_UVB}. Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
